Optimal Particle Paths Around Points in $\R^2$ with Constrained Acceleration

### 2013-09-29 path_theorems.tex
Add proof of minimizing theta.

\begin{proof}
Since $\theta(T_{f,\gamma}) = 0$, then if $\frac{d\abs{\theta(t)}}{dt} > 0$ at some point along the path, then $\theta{T_{f,\gamma}} < \theta{t_0} < \theta{t_c}$, so [TODO]
\end{proof}

>>>>

\begin{proof}
Since $\theta(T_{f,\gamma}) = 0$, then if $\frac{d\abs{\theta(t)}}{dt} > 0$ for $t \in [t_1, t_2]$, since $\theta{T_{f,\gamma}} < \theta{t_1}$, then by Lemma \ref{lemma:intermediate-theta} $\theta(t_1) = \theta(t_2)$ for some $t_2 \in [t_1, T_{f, \gamma}$. Since all of the time derivatives in (\ref{eq:r-deriv}) - (\ref{eq:theta-deriv}) are all monotonic for $r \in (0, \infty)$, there is no local maximum for them, so the optimal strategy should be the same, regardless of $r$. In other words, there can not be multiple cases for optimal strategies based on $r$.
\end{proof}
